\Large On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory

### 2025-06-09 MasterDefense/main.tex
Newest

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{slashed}
\usepackage[most]{tcolorbox}

@@

\begin{frame}
    \frametitle{Challenges we face befor}
\begin{center}

@@

\end{tikzpicture}
\end{center}
\vspace{-2.3em}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
$n=$ & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
\hline
     & 4 & 25 & 220 & 2485 & 34300 & 559405 & 10525900 \\
\hline
\end{tabular}
\end{center}
\pause

The answer is On-shell method.
    \begin{center}

@@

% Text Node
\draw (233.4,128.25) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
% Text Node
\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
% Text Node
\draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};

\end{tikzpicture}
\end{center}
\end{frame}
\section{Preliminary}
\begin{frame}
    \frametitle{Conventional VS. Modern}
    Usually, when we compute the gluon amplitudes by using Feynman diagram, we will obtain something like 
\begin{equation*}
    \begin{aligned}
&\mathcal{M}_s(p_1 p_2 \to p_3 p_4) = - \frac{g_s^2}{s} f^{abe} f^{cde} \\
&\quad \times \Big\{ 
-4\, \epsilon_1 \cdot \epsilon_3^* \, \epsilon_2 \cdot p_1 \, \epsilon_4^* \cdot p_3 
+ 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_1 \, \epsilon_4^* \cdot p_3 \\
&\quad - 2\, \epsilon_1 \cdot p_4 \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*
+ \epsilon_1 \cdot \epsilon_2 \, p_4 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^* \\
&\quad + 4\, \epsilon_1 \cdot \epsilon_4^* \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot p_4 
- 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_4 \, \epsilon_4^* \cdot p_1 \\
&\quad - 2\, \epsilon_1 \cdot p_2 \, \epsilon_2 \cdot p_3 \, \epsilon_3^* \cdot \epsilon_4^*
+ \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot \epsilon_4^* \, p_2 \cdot p_3 \\
&\quad + 4\, \epsilon_1 \cdot p_2 \, \epsilon_2 \cdot \epsilon_3^* \, \epsilon_4^* \cdot p_3 
- 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_2 \, \epsilon_4^* \cdot p_3 \\
&\quad + 2\, \epsilon_1 \cdot p_2 \, \epsilon_2 \cdot p_4 \, \epsilon_3^* \cdot \epsilon_4^* 
- \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot \epsilon_4^* \, p_4 \cdot p_2 \\
&\quad + 2\, \epsilon_1 \cdot p_3 \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^* 
- \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot \epsilon_4^* \, p_1 \cdot p_3 
\Big\}.
\end{aligned}
\end{equation*}
\end{frame}
\begin{frame}
    If you consider 5point case, it will become worser:
\begin{center}
    \textcolor{red}{$\bigstar$ There are nearly 10000 terms!}
\end{center}
\begin{columns}[T,onlytextwidth]
    % 左侧：传统图像
    \column{0.48\textwidth}
    \textbf{传统费曼图计算：}
    \begin{figure}
        \centering
        \includegraphics[width=\linewidth]{5pt.png}
    \end{figure}
    \pause 
    % 右侧：PT表达式
    \column{0.48\textwidth}
    \vspace{1.5em}
    \qquad \textbf{Parke–Taylor Formula:}
    \begin{gather*}
        \textcolor{red}{A_5(1^-,2^-,3^+,4^+,5^+)} =\\
        \textcolor{red}{\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}
    \end{gather*}
\end{columns}
\vspace{2em}
\textcolor{red}{$\bigstar$ \Large It becomes quite simple and compact!}
\end{frame}
\begin{frame}
    \frametitle{Fantasitic result from Cauchy Theorem}
    %First, I will show the most important part in this report.
    \begin{block}{BCFW recursion relation}
        \begin{equation*}
            A_n=\sum_{\text{diagrams}\,I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=\sum_{\text{diagrams}\,I}\raisebox{-1.3em}{\includegraphics[height=3em]{recrel1.pdf}}
        \end{equation*}
    \end{block}
\vspace*{1em}
\pause
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

@@

\textcolor{red}{$\bigstar $ ~ From lower point to higher point!!}

\end{frame}
\begin{frame}{Spinor-Helicity Formalism}
\begin{block}{Helicity}
\textbf{Helicity} is defined as the projection of a particle's spin vector $\vec{S}$ onto the direction of its momentum $\vec{p}$:
\[
h = \frac{\vec{S} \cdot \vec{p}}{|\vec{p}|}
\]
\end{block}
\pause
% 文本说明（点击1出现）
\only<1->{
S-matrix is a function of momentum $p_i$ and helicity $h_i$
}

@@

\begin{frame}
    It has been proposed that this model actually discretized \textcolor{red}{a five-dimension gauge theory} with gauge group $SU(m)$, where 
    only the fifth dimension are latticed. So it is an effective theory for 5d gauge theory.
     \vspace{1em} % 图与文字之间的间距
    \begin{center}
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\linewidth]{Moosed.jpeg} % ← 替换为你的图片文件名
        \par\vspace{0.5em}
    \end{minipage}
    \hspace{0.05\textwidth}
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\linewidth]{Lattice.jpg} % ← 替换为你的图片文件名
        \par\vspace{0.5em}
    \end{minipage}
    \end{center}
    \pause
    After higgsing the scalar field, we can obtain a spectrum
    \begin{equation*}
        M_k^2=4g^2f_s^2\sin^2\left(\frac{\pi k}{N}\right)
    \end{equation*}
    This is precisely the \textcolor{red}{Kaluza-Klein} spectrum under $S^2$ compactification. 
\end{frame}
\begin{frame}
    \frametitle{Scattering Amplitudes from BCFW}
    For simplicity, we start from the two-site gauge theory with gauge fields $V_1$, $V_2$ and scalar fields $\Phi$, $\Phi^\dagger$.
    \begin{equation*}
        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_1)^2-\frac{1}{2}\mathrm{Tr}(F_2)^2+\mathrm{Tr}[(D_\mu\Phi)^\dagger(D^\mu\Phi)],
    \end{equation*}
We only foucus on the following amplitudes:
\begin{equation*}
    \textcolor{red}{nV_1,\qquad nV_2,\qquad\Phi^\dagger nV_1 \Phi,\qquad \Phi nV_2 \Phi^\dagger,\qquad \Phi^\dagger \Phi\Phi^\dagger \Phi}
\end{equation*}
here n can be any positive integer.
\end{frame}
\begin{frame}
    \frametitle{Basic building block -- 3-point}
    From the previous section, we have known that there are only two kinds of 3 point amplitude
    \begin{gather*}
        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
    \end{gather*}
    By using the 3 point building block, we can construct 4 point color-ordered amplitudes from BCFW recursion relation.
\end{frame}
\begin{frame}
    \frametitle{Gauge boson sector}
    \begin{itemize}
        \item n$ V_1$ or n$V_2$\\
        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
        existing results.
        \begin{equation*}
            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
        \end{equation*}
        \textcolor{red}{Notice that this formula only applies to MHV amplitudes, although the NMHV can be completely solved.}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{SQCD like sector}
    \begin{itemize}
        \item $\Phi^\dagger V_1V_1\Phi$\\
        Here we compute the color-ordered amplitude $A[1,2,3^+,4^-]$. We choose $[2,3\rangle$ shift
        \begin{gather*}
        \hat{\sket{2}}=\sket{2}-z\sket{3},\qquad \hat{\aket{2}}=\aket{2} \\
        \hat{\sket{3}}=\sket{3},\qquad \hat{\aket{3}}=\aket{3}+z\aket{2}
        \end{gather*}
        The amplitudes can be computed 
        \begin{align*}
            A[1,2,3^+,4^-]=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
        \end{align*}
        \item $\Phi^\dagger V_1V_1V_1\Phi$
            \begin{equation*}
                A[1,2,3^+,4^+,5^-]=\frac{\avg{15}^2\!\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
            \end{equation*}
    \end{itemize}
\end{frame}

    \end{itemize}
\end{frame}
\section{Summary}
\begin{frame}
    \frametitle{Summary}
    \begin{itemize}
        \item Introduce the on-shell method, including BCFW recursion relation, spinor-helicity formalism, etc.
        \item Introduce a (de)constructed gauge theory model, which is an effective field theory for 5 dimension gauge theory.
        \item Much of the scattering amplitudes in this model can be recursively computed by BCFW, and some compact formulas are offered.
    \end{itemize}
\end{frame}
\begin{frame}
    \centering
    \Huge Thanks for your attention!
\end{frame} 
\appendix

@@

    \textbf{Example}: 3-gluon amplitude\\
    \begin{equation*}
        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
    \end{equation*}
\end{frame}
\end{document}

>>>>

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{slashed}
\usepackage[most]{tcolorbox}
\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{arrows.meta, positioning}

@@

\begin{frame}
    \frametitle{Challenges we face before}
\begin{center}

@@

\end{tikzpicture}
\end{center}
\vspace{-2.3em}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
$n$ pt. amplitudes & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
\hline
\# of diag.      & 4 & 25 & 220 & 2485 & 34300 & 559405 & 10525900 \\
\hline
\end{tabular}
\end{center}
\pause
\centering
\textcolor{red}{The number of Feyman diagrams grow quite rapidly!}

\begin{frame}
\frametitle{Conventional Computation}
\hypertarget{conv}{}
    Usually, when we compute the gluon amplitudes by using Feynman diagram, we will obtain something like 
\begin{figure}
  \centering
  \includegraphics[height=2.5cm]{4ptt2.pdf} \hfill
  \includegraphics[height=2.8cm]{4ptt2_1.pdf}
\end{figure}

\vspace{-2em}
\hyperlink{helicity}{
\begin{flushleft}
$
\begin{aligned}
&\mathcal{M}_s(p_1 p_2 \to p_3 p_4) = - \frac{g_s^2}{s} f^{abe} f^{cde} \\
&\quad \times \Big\{ 
-4\, \epsilon_1 \cdot \epsilon_3^* \, \epsilon_2 \cdot p_1 \, \epsilon_4^* \cdot p_3 
+ 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_1 \, \epsilon_4^* \cdot p_3 \\
& \quad - 2\, \epsilon_1 \cdot p_4 \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*
+ \epsilon_1 \cdot \epsilon_2 \, p_4 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*  + \text{remaining 10 terms}\big\}
\end{aligned}
$
\end{flushleft}
}
\end{frame}

\begin{frame}
If you consider 5point case, it will become worse:
\begin{center}
    \textcolor{red}{$\bigstar$ We have 25 diagrams and nearly 10000 terms!}
\end{center}
\vspace{-2em}
    % 左侧：传统图像

    \textbf{传统费曼图计算：}
    \begin{figure}
        \centering
        \includegraphics[width=0.5\linewidth]{5pt.png}
    \end{figure}
\vspace{-1.5em}
\pause
\begin{center}
\hspace*{-0.5em}\includegraphics[width=1.05\textwidth]{structure.png}
\end{center}
\vspace{-1.5em}
\pause
\hspace*{-0.5em}\textcolor{red}{We need to cancel many useless information because of gauge redundancies!}

\end{frame}
\section{Preliminary}
\begin{frame}
\frametitle{Modern Amplitude Method} 
 The answer is On-shell method.
    \begin{center}

@@

% Text Node
\draw (233.4,128.25) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
% Text Node
\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
% Text Node
\draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};
\end{tikzpicture}
\end{center}
\vspace{-1em}
\pause
$M_5=\!\!\!\!\!\!\underbrace{A_5[12345]}_{\textcolor{red}{\text{Color-ordered Amplitudes}}}\mathrm{Tr}[T^{a_1}T^{a_2}\cdots T^{a_5}]+\text{perms}$ ,\quad$+,-$ : helicity

    % 右侧：PT表达式

    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
    \begin{gather*}
        {A_5[1^+,2^+,3^+,4^+,5^+]=0}\\
        {A_5[1^-,2^+,3^+,4^+,5^+]=0}\\
        \textcolor{red}{A_5[1^-,2^-,3^+,4^+,5^+]=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trival one})\\
    \end{gather*}
    \vspace{-3em}
    \pause
    \begin{gather*}
        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}_\alpha[\lambda|_{\dot{\alpha}},\quad \sigma^\mu=(1,\vec{\sigma}),\\
        \aket{\lambda},\sket{\lambda}: \text{Weyl Spinors}
    \end{gather*}
\end{frame}

\begin{frame}
    \frametitle{Modern Amplitude Method} 
 The answer is On-shell method.
    \begin{center}

% Text Node
\draw (233.4,128.25) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
% Text Node
\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
% Text Node
\draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};
\end{tikzpicture}
\end{center}
\vspace{-1em}
    % 右侧：PT表达式
    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
    \begin{gather*}
        {A_5[1^+,2^+,3^+,4^+,5^+]=0}\\
        {A_5[1^-,2^+,3^+,4^+,5^+]=0}\\
        \textcolor{red}{A_5[1^-,2^-,3^+,4^+,5^+]=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trival one})\\
    \end{gather*}
    \vspace{-2em}
    \begin{gather*}
        {A_5[1^-,2^-,3^-,4^-,5^-]=0}\\
        {A_5[1^+,2^-,3^-,4^-,5^-]=0}\\
        \textcolor{red}{A_5[1^+,2^+,3^-,4^-,5^-]=\frac{[12]^4}{[12][23][34][45][51]}}
    \end{gather*}
\end{frame}

\begin{frame}
    \frametitle{The Power of BCFW Recursion Relation}
    %First, I will show the most important part in this report.
    \begin{block}{BCFW recursion relation}
        \begin{equation*}
            A_n=\sum_{\text{diagrams}\,I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=\sum_{\text{diagrams}\,I}\raisebox{-1.3em}{\includegraphics[height=3em]{recrel1.pdf}}
        \end{equation*}
    \end{block}
\vspace*{1em}
\pause
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

@@

\textcolor{red}{$\bigstar $ ~ From lower point on-shell amp. to higher point on-shell amp.!!}

\begin{frame}
    More specifically,

\begin{center}
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

%Straight Lines [id:da4236245229594603] 
\draw    (259,91.9) -- (308,92.24) ;
\draw [shift={(310,92.25)}, rotate = 180.39] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da22408043084764206] 
\draw    (341.2,91.9) -- (391,91.76) ;
\draw [shift={(393,91.75)}, rotate = 179.83] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da5239716133788715] 
\draw    (421.7,91.3) -- (477,91.73) ;
\draw [shift={(479,91.75)}, rotate = 180.45] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

% Text Node
\draw (231.8,83.1) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont 3pt.}};
% Text Node
\draw (313.5,83) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont 4pt.}};
% Text Node
\draw (396.9,83.5) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont 5pt.}};
% Text Node
\draw (482.4,85.2) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};
% Text Node
\draw (214,107.4) node [anchor=north west][inner sep=0.75pt]  [font=\small]  {$\frac{\langle 12\rangle ^{4}}{\langle12\rangle\langle 23\rangle \langle 31\rangle }$};
% Text Node
\draw (279.25,107.4) node [anchor=north west][inner sep=0.75pt]  [font=\small]  {$\frac{\langle 12\rangle ^{4}}{\langle 12\rangle \langle 23\rangle \langle 34\rangle \langle 41\rangle }$};
% Text Node
\draw (370.75,107.4) node [anchor=north west][inner sep=0.75pt]  [font=\small]  {$\frac{\langle 12\rangle ^{4}}{\langle 12\rangle \langle 23\rangle \langle 34\rangle \langle 45\rangle \langle 51\rangle }$};

\pause
\begin{equation*}
    \boxed{\Rightarrow:\quad A[1^+\cdots ~i^-,(i+1)^+\cdots~j^-\cdots n^+]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
\end{equation*}

\vspace*{2em}
\textcolor{red}{$\bigstar$ \Large This is the power of BCFW recursion relation.}
\end{frame}
\begin{frame}{From Review to Applications}

\begin{columns}[T]
  % 左列：当前已完成
  \begin{column}{0.48\textwidth}
    \begin{block}{\centering\large \textbf{So far: Foundations}}
      \begin{itemize}[left=1em]
        \item Reviewed the structure of \textbf{BCFW recursion relation}
        \item Applied to:
          \begin{itemize}[left=0.1em]
            \item \textbf{Pure Yang-Mills} theory
            \item Tree-level MHV amplitudes
            \item Color-ordered partial amplitudes
          \end{itemize}
      \end{itemize}
    \end{block}
  \end{column}
\pause
  % 右列：研究目标
  \begin{column}{0.48\textwidth}
    \begin{block}{\centering\large \textbf{Next: Realistic Models}}
      \begin{itemize}[left=1em]
        \item Move beyond massless gauge theory
        \item Consider:
          \begin{itemize}[left=0.1em]
            \item \textbf{(De)constructed gauge theories}
          \end{itemize}
        \item Key questions:
          \begin{itemize}[left=0.1em]
            \item Can BCFW still apply?
            \item How to choose momentum shift?
            \item What new structures emerge?
          \end{itemize}
      \end{itemize}
    \end{block}
  \end{column}
\end{columns}

\begin{frame}
    It has been proposed that this model actually discretized \textcolor{red}{a five-dimension gauge theory} with gauge group $SU(m)$, where 
    only the fifth dimension are latticed. So it is an effective theory for 5d gauge theory.
     \vspace{1em} % 图与文字之间的间距
    \begin{center}
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\linewidth]{Moosed.jpeg} % ← 替换为你的图片文件名
        \par\vspace{0.5em}
    \end{minipage}
    \hspace{0.05\textwidth}
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\linewidth]{Lattice.jpg} % ← 替换为你的图片文件名
        \par\vspace{0.5em}
    \end{minipage}
    \end{center}
    \pause
    After higgsing the scalar field, we can obtain a spectrum
    \begin{equation*}
        M_k^2=4g^2f_s^2\sin^2\left(\frac{\pi k}{N}\right)
    \end{equation*}
    This is precisely the \textcolor{red}{Kaluza-Klein} spectrum under $S^1$ compactification. 
\end{frame}

\begin{frame}
    \frametitle{Amplitudes from BCFW}
    \begin{figure}
        \centering
        \includegraphics[width=0.5\textwidth]{2-site.png}
    \end{figure}
    \vspace{-1em}
    From the previous section, we have known that there are only two kinds of 3 point amplitude
    \begin{gather*}
        A[1^\Phi,2^{\Phi^\dagger},3^+]=\frac{[23][31]}{[12]},\qquad A[1^\Phi,2^{\Phi^\dagger},3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
    \end{gather*}
    By using the 3 point building block, we can construct 4 point colorordered amplitudes from BCFW recursion relation.
\end{frame}
\begin{frame}
    \frametitle{Gauge boson sector}
    \begin{itemize}
        \item n$ V_1$ or n$V_2$\\
        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
        existing results.
        \begin{equation*}
            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
        \end{equation*}
        \textcolor{red}{Notice that this formula only applies to MHV amplitudes, although the NMHV can be completely solved.}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{SQCD like sector}
    \begin{itemize}
        \item $\Phi^\dagger V_1V_1\Phi$\\
        Here we compute the color-ordered amplitude $A[1,2,3^+,4^-]$. We choose $[2,3\rangle$ shift
        \begin{gather*}
        \hat{\sket{2}}=\sket{2}-z\sket{3},\qquad \hat{\aket{2}}=\aket{2} \\
        \hat{\sket{3}}=\sket{3},\qquad \hat{\aket{3}}=\aket{3}+z\aket{2}
        \end{gather*}
        The amplitudes can be computed 
        \begin{align*}
            A[1,2,3^+,4^-]=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}\quad (\textcolor{red}{\text{Parke -Talyor like Formula}})
        \end{align*}
        \item $\Phi^\dagger V_1V_1V_1\Phi$
            \begin{equation*}
                A[1,2,3^+,4^+,5^-]=\frac{\avg{15}^2\!\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
            \end{equation*}
    \end{itemize}
\end{frame}

    \end{itemize}
    \pause
    For example, if we want to compute $A[1,2,5_1^+,3_1^+,4_1^-,7_2^+,6_2^+,8_2^+]$:
    \begin{equation*}
        A=\frac{\avg{2\textcolor{green}{4}}^2\avg{1\textcolor{green}{4}}^2}{\textcolor{blue}{\mdavg{25}{53}\mdavg{34}{41}}\textcolor{red}{\mdavg{27}{76}\mdavg{68}{81}}}
    \end{equation*}
\end{frame}
\section{Summary}
\begin{frame}
    \frametitle{Summary}
    \begin{itemize}
        \item Introduce the on-shell method, including BCFW recursion relation, spinor-helicity formalism, etc.
        \item Introduce a (de)constructed gauge theory model, which is an effective field theory for 5 dimension gauge theory.
        \item Much of the scattering amplitudes in this model can be recursively computed by BCFW, and some compact formulas are offered.
    \end{itemize}
\end{frame}
\begin{frame} 
    \centering
    \Huge Thanks for your attention!
\end{frame} 
\appendix
\begin{frame}{Spinor-Helicity Formalism}
    \hypertarget{helicity}{}
\begin{block}{Helicity}
\textbf{\hyperlink{conv}{Helicity}} is defined as the projection of a particle's spin vector $\vec{S}$ onto the direction of its momentum $\vec{p}$:
\[
h = \frac{\vec{S} \cdot \vec{p}}{|\vec{p}|}
\]
\end{block}
\pause
% 文本说明（点击1出现）
\only<1->{
S-matrix is a function of momentum $p_i$ and helicity $h_i$
}

@@

@@

    \textbf{Example}: 3-gluon amplitude\\
    \begin{equation*}
        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
    \end{equation*}
\end{frame}

\begin{frame}
    \frametitle{Scattering Amplitudes from BCFW}
    For simplicity, we start from the two-site gauge theory with gauge fields $V_1$, $V_2$ and scalar fields $\Phi$, $\Phi^\dagger$.
    \begin{equation*}
        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_1)^2-\frac{1}{2}\mathrm{Tr}(F_2)^2+\mathrm{Tr}[(D_\mu\Phi)^\dagger(D^\mu\Phi)],
    \end{equation*}
We only foucus on the following amplitudes:
\begin{equation*}
    \textcolor{red}{nV_1,\qquad nV_2,\qquad\Phi^\dagger nV_1 \Phi,\qquad \Phi nV_2 \Phi^\dagger,\qquad \Phi^\dagger \Phi\Phi^\dagger \Phi}
\end{equation*}
here n can be any positive integer.
\end{frame}

\end{document}
